Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-22 paper/paper.tex
He et al. 2018 reference

% (sparsity tech large-scale models) gale-elsen-hooker.tex
\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
and outperform pruning on the studied architectures, overall pruning is preferable due to
simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
consistent performance and are more complex, they induce non-uniform sparsity throughout
the model, which is essential for better compression \verify{(He et al., 2018)}.
%
% Magnitude pruning induces user-specified sparsity distributions.
%
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
%
Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}

>>>>

% (sparsity tech large-scale models) gale-elsen-hooker.tex
\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
and outperform pruning on the studied architectures, overall pruning is preferable due to
simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
consistent performance and are more complex, they induce non-uniform sparsity throughout
the model, which is essential for better compression \citep{he_amc:_2018}.
\todo{read (He et al., 2018)}
%
% Magnitude pruning induces user-specified sparsity distributions.
%
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
%
Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}
